Additional Tables

### 2019-08-12 notebooks/article_notebook2.Rmd
added package ref

| Package       | Version | Reference |
|---------------|---------|-----------|
| dplyr         | 0.8.0.1 |   [2]     |
| tidyr         | 0.8.3   |   [3]     |
| ggplot2       | 3.1.1   |   [4]     |
| purrr         | 0.3.2   |   [5]     |
| tibble        | 2.1.1   |   [6]     |
| Biostrings    | 2.50.2  |   [7]     |
| vegan         | 2.5.4   |   [8]     |
| stringr       | 1.4.0   |   [9]     |
| cluster       | 2.0.8   |   [10]    |
| ape           | 5.3     |   [11]    |
| ggtree        | 1.14.6  |   [12]    |
| RColorBrewer  | 1.1-2   |   [13]    |
| cowplot       | 0.9.4   |   [14]    |
| knitr         | 1.22    |   [15]    |
| kableExtra    | 1.1.0   |   [16]    |
| ggsci         | 2.9     |   [17]    |
| fastqcr       | 0.1.2   |   [18]    |
| scales        | 1.0.0   |   [19]    |
| viridis       | 0.5.1   |   [20]    |

@@

>>>>

| Package       | Version | Reference |
|---------------|---------|-----------|
| dplyr         | 0.8.0.1 |   [2]     |
| tidyr         | 0.8.3   |   [3]     |
| ggplot2       | 3.1.1   |   [4]     |
| purrr         | 0.3.2   |   [5]     |
| tibble        | 2.1.1   |   [6]     |
| Biostrings    | 2.50.2  |   [7]     |
| vegan         | 2.5.4   |   [8]     |
| stringr       | 1.4.0   |   [9]     |
| cluster       | 2.0.8   |   [10]    |
| ape           | 5.3     |   [11]    |
| ggtree        | 1.14.6  |   [12]    |
| RColorBrewer  | 1.1-2   |   [13]    |
| cowplot       | 0.9.4   |   [14]    |
| knitr         | 1.22    |   [15]    |
| kableExtra    | 1.1.0   |   [16]    |
| ggsci         | 2.9     |   [17]    |
| fastqcr       | 0.1.2   |   [18]    |
| scales        | 1.0.0   |   [19]    |
| viridis       | 0.5.1   |   [20]    |
| adephylo      | 1.1-11  |   [21]    |

@@

[21] Jombart T., Dray S. (2008) adephylo: exploratory analyses for the phylogenetic comparative method.
